Seismic Hazard Estimation of Northern Iran Using Smoothed Seismicity

### 2016-10-20 introduction.tex
done with introduction for now.

\myrevision{In the present study, we focus our attention on northern Iran. This region houses about 41 percent (32 million) of the total population of the country, with most living in the cities of Tehran, Mashhad, Tabriz, Karaj, Qom, Urmia, Rasht, and Ardabil. This region has suffered multiple devastating earthquakes in the past \citep[e.g.,][]{Mehrain_1990_Tech, Chafory-Ashtiany_1999_DPM, Razzaghi_2012_Tech}, and has recently been the subject of various efforts to better characterize seismic hazard \citep[e.g.,][]{Abdollahzadeh2014a, Boostan2015}. Among other things, these studies have highlighted the prevailing differences between alternative approaches, the importance of quantifying uncertainty, and the need for considering all potential faults in the region---even if believed inactive---by adopting new methodologies and the latest available data.}

\myrevision{Most previous studies for northern Iran focus on particular locations based on specific categorization of seismogenic faults \citep[e.g.][]{Ghodrati2003,Vafaie2011,Abdi2013}, which are often subjectively interpreted and limited to data availability. By contrast, we use an approach based on the smoothed seismicity method introduced by \citet{Frankel1995}. We use regionally-based and smoothed seismic parameters derived from an up-to-date seismic catalog, use an appropriate attenuation relationship, and consider various levels of uncertainty.} The smoothed seismicity approach has been used with success in other regions \citep[e.g.][]{Cao1996, Akinci2004, Kalkan2009}, including Iran \citep{Khodaverdian_2016_BSSA}. \myrevision{In \citep{Khodaverdian_2016_BSSA}, the seismic parameters $b$ and $M_{\max}$ are calculated for sites equally distributed all over the Iran on a grid 1*1 degree. Earthquake catalog for each grid point is all events within 200 km buffer zone surrounding the grid point. Whereas in this study, we assume the seismic parameters are uniform for each tectonic seismic region.} Its major feature is the treatment of cataloged instrumental and historical earthquakes as individual point sources as opposed to events that are part of a predefined system of faults in a given tectonic setting. While we recognize that \myrevision{fault-based/geologic-based earthquake recurrence estimates} can be more realistic and accurate, by choosing the smoothed seismicity method we seek to \myrevision{acknowledge} the uncertainty associated with fault mapping, earthquake location and source mechanism definitions, and to cover areas that would otherwise be underestimated or ignored. In our analysis, we assume earthquake hazard in northern Iran to be dominated by the seismic zones of Azerbaijan, Alborz, and Kopeh-Dagh, but also consider the contribution of the areas of Zagros and the central-east seismic zones to the hazard calculation within our domain of interest (see Fig.~\ref{fig:iran}). In addition to this five seismic-zone model, we obtain results for the entire region of interest as if it could be considered as a single uniform seismic zone. We used both these models and the combination of them to interpret seismic hazard in northern Iran.

In the following sections we describe our region of interest in greater detail, review its associated tectonics and seismicity, and provide additional information about the adopted approach. Significant aspects of our work include the composition of the earthquake catalog, including catalog completeness and the conversion of earthquake magnitudes, the selection of an appropriate attenuation relationship for the region, and the estimation of the Gutenberg-Richter seismicity parameters. Our analysis includes seismic hazard curves and maps for peak ground acceleration (PGA) considering exceedance probabilities of 2 and 10 percent in 50 years for rock site conditions for events with moment magnitude \myrevision{$M_w \geq 4.5$}. We analyze our results in light of similar estimates available in the literature and summarize the most relevant conclusions.

>>>>

\myrevision{In the present study, we focus our attention on northern Iran. This region houses about 41 percent (32 million) of the total population of the country, with most living in the cities of Tehran, Mashhad, Tabriz, Karaj, Qom, Urmia, Rasht, and Ardabil. This region has suffered multiple devastating earthquakes in the past \citep[e.g.,][]{Mehrain_1990_Tech, Chafory-Ashtiany_1999_DPM, Razzaghi_2012_Tech}, and has recently been the subject of various efforts to better characterize seismic hazard \citep[e.g.,][]{Abdollahzadeh2014a, Boostan2015}. Among other things, these studies have highlighted the prevailing differences between alternative approaches, the importance of quantifying uncertainty, and the need for considering all potential faults---even if believed inactive---by adopting new methodos and the latest available data.}

\myrevision{Most previous studies for northern Iran focus on particular locations based on specific seismogenic faults \citep[e.g.][]{Ghodrati2003,Vafaie2011,Abdi2013}, which are often subjectively interpreted and limited to data availability. By contrast, we use an approach based on the smoothed seismicity method introduced by \citet{Frankel1995}. We use regionally-based, smoothed seismic parameters derived from an up-to-date seismic catalog, and an appropriate attenuation relationship.} The smoothed seismicity approach has been used with success in other regions \citep[e.g.][]{Cao1996, Akinci2004, Kalkan2009}, including Iran \citep{Khodaverdian_2016_BSSA}. Its major feature is the treatment of cataloged instrumental and historical earthquakes as individual point sources as opposed to events that are part of a predefined system of faults in a given tectonic setting. While we recognize that \myrevision{fault-based or geology-based earthquake recurrence estimates} can be more realistic and accurate, by choosing the smoothed seismicity method we seek to \myrevision{acknowledge} the uncertainty associated with fault mapping, earthquake location and source mechanism definitions, and to cover areas that would otherwise be underestimated or ignored. In our analysis, we assume earthquake hazard in northern Iran to be dominated by the seismic zones of Azerbaijan, Alborz, and Kopeh-Dagh, but also consider the contribution of the areas of Zagros and the central-east seismic zones to the hazard calculation within our domain of interest (see Fig.~\ref{fig:iran}). In addition to this five seismic-zone model, we obtain results for the entire region of interest as if it could be considered as a single uniform seismic zone. We used both these models, \myrevision{and different levels of uncertainty in the seismic parameters and ground motion prediction equation, to combine the results using a logic tree} to interpret seismic hazard in northern Iran.

In the following sections we describe our region of interest in greater detail, review its associated tectonics and seismicity, and provide additional information about the adopted approach. \myrevision{Our results are summarized in terms of seismic hazard curves and maps for peak ground acceleration (PGA) considering exceedance probabilities of 2 and 10 percent in 50 years for rock site conditions for events with moment magnitude \myrevision{$M_w \geq 4.5$}, which we analyze in light of similar estimates available in the literature.}
